%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Academic Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {Carleton University} % Organization
    {Ottawa, Canada} % Location
    {Apr.~2019 -- Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Member of the \href{https://www.cisl.carleton.ca/}{CCSL/CISL} research group.
        \item Researching Extended BPF for runtime security implementations under the Linux kernel.
        \item Co-supervised by \href{https://people.scs.carleton.ca/~soma/}{Dr.~Anil Somayaji}
          and \href{https://dbarrera.xyz/}{Dr.~David Barrera}.
        \item Designed and developed ebpH, an anomaly detection system for Linux, using eBPF.
        \begin{itemize}
          \item This work was the subject of my undergraduate
            \href{https://www.cisl.carleton.ca/~will/written/coursework/undergrad-ebpH-thesis.pdf}
              {Honours Thesis}.
        \end{itemize}
        \item Designed and developed bpfbox, a process confinement tool for Linux, using eBPF.
        \begin{itemize}
          \item This work was \href{https://dl.acm.org/doi/10.1145/3411495.3421358}{published at ACM CCSW'2020}.
        \end{itemize}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Teaching Assistant, COMP3000 Operating Systems} % Job title
    {Carleton University} % Organization
    {Ottawa, Canada} % Location
    {Sept.~2018 -- Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Nominee for the \href{https://carleton.ca/tasupport/taawards/edc-outstanding-ta-awards/}
            {Outstanding Teaching Assistant Award} in the 2018/2019, 2019/2020, and 2020/2021 academic years.
        \item Ran tutorial sessions for groups of 50 students.
        \item Took a leadership role to ensure tutorials proceeded smoothly.
        \item Held weekly office hours and workshops for students.
        \item Graded assignments and tests and gave appropriate feedback.
        \item Developed a \href{https://github.com/willfindlay/tabot}{Discord bot} to help manage the class Discord server, used during the COVID-19 pandemic.
        \item Developed new tutorials which are now used each semester:
          \begin{itemize}
            \item \href{https://homeostasis.scs.carleton.ca/wiki/index.php/Operating_Systems_2020W:_Tutorial_6}
              {Concurrency tutorial}
            \item \href{https://homeostasis.scs.carleton.ca/wiki/index.php/Operating_Systems_2020W:_Tutorial_8}
              {Kernel memory management tutorial}
            \item \href{https://homeostasis.scs.carleton.ca/wiki/index.php/Operating_Systems_2020W:_Tutorial_9}
              {eBPF tutorial}
            \item \href{https://homeostasis.scs.carleton.ca/wiki/index.php/Operating_Systems_2019F:_Tutorial_9}
              {Rootkit tutorial}
          \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
